---
title: "InnerSource Obstacles"
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
    fig_crop: no
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(plyr)
library(likert)
library(shiny.i18n)
library(stringr)
require(showtext)

showtext_auto()

i18n <- Translator$new(translation_csvs_path = "./data")
i18n$set_translation_language("中文")

process.lik = function(x){
  return(factor(x, levels = c('0','1','2','3','4','5','6','7','8','9','10')))
}

f.dev = ldply(list.files(path = 'result/survey', pattern = 'Developer', full.names = T), read.csv, header=T)
f.man = ldply(list.files(path = 'result/survey', pattern = 'Manager', full.names = T), read.csv, header=T)
f.own = ldply(list.files(path = 'result/survey', pattern = 'Owner', full.names = T), read.csv, header=T)
```

<!-- ```latex -->
<!-- \usepackage{ctex} -->
<!-- ``` -->

# `r  i18n$t("Results of InnerSource Obstacles Survey")`

## `r i18n$t("Obstacles noted by the Managers")`

### `r i18n$t("From Survey Questions")`

```{r echo=FALSE, fig.show="hold", out.width="90%", fig.align="center", fig.width=12, fig.height=7}
what = i18n$t("Don't know what InnerSource is")
benefit = i18n$t("Not sure about the benefits of InnerSource")
resource = i18n$t("Lack of resource to allow cross-contribution")
quality = i18n$t("Unsure about Quality of outsider contributions")
responsible = i18n$t("Customer Service Impact from not knowing buggy code creator")
man_struct = i18n$t("Potential change in Management structure disrupting workflow")
budget = i18n$t("Budget Allocation for InnerSource")

colnames(f.man) = c('type', 'name', what, benefit, resource, quality, responsible, man_struct, budget, 'Other', 'One positive thing')
lv = data.frame(lapply(f.man[,3:9], process.lik))
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=17)) + guides(fill=guide_legend(""))+ ggtitle(paste0('N=',nrow(f.man)))

```

### `r i18n$t("Other Obstacles")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.man$Other), collapse = "\n")))

```

### `r i18n$t("One positive thing about InnerSource")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.man$`One positive thing`), collapse = "\n")))

```

## `r i18n$t("Obstacles noted by the Repository Owners")`

### `r i18n$t("From Survey Questions")`

```{r echo=FALSE, fig.show="hold", out.width="90%", fig.align="center", fig.width=12, fig.height=7}
patcher = i18n$t("Lack of Patchers")
responsibility = i18n$t("Unsure about the Responsibilities")
mentor = i18n$t("Lack of time for Mentoring")
steal = i18n$t("Code 'Stolen' without proper credit")
publish = i18n$t("Don't want to publish code for InnerSource")
good = i18n$t("Don't know what's appropriate for InnerSource")
manager = i18n$t("Lack of support from Line Manager")
learn = i18n$t("Steep Learning Curve")
breaking = i18n$t("Breaking Changes affecting unknown consumers")
incentive = i18n$t("Incentives aren't appropriate")
  
colnames(f.own) = c('type', 'name', quality, patcher, responsibility, mentor, steal, publish, good, manager, learn, breaking, incentive, 'Other', 'One positive thing')
lv = data.frame(lapply(f.own[,3:13], process.lik))
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=17)) + guides(fill=guide_legend(""))+ ggtitle(paste0('N=',nrow(f.own)))

```

### `r i18n$t("Other Obstacles")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.own$Other), collapse = "\n")))

```

### `r i18n$t("One positive thing about InnerSource")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.own$`One positive thing`), collapse = "\n")))

```

## `r i18n$t("Obstacles noted by the Developers")`

### `r i18n$t("From Survey Questions")`

```{r echo=FALSE, fig.show="hold", out.width="90%", fig.align="center", fig.width=12, fig.height=7}
howc = i18n$t("Don't know how to contribute to InnerSource")
timel = i18n$t("Don't have time to contribute to InnerSource")
project = i18n$t("Project are uninteresting")
judge = i18n$t("Being judged for mistakes")

colnames(f.dev) = c('type', 'name', what, howc, manager, incentive, timel, learn, project, judge, 'Other', 'One positive thing')
lv = data.frame(lapply(f.dev[,3:10], process.lik))
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=17)) + guides(fill=guide_legend(""))+ ggtitle(paste0('N=',nrow(f.dev)))


```

### `r i18n$t("Other Obstacles")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.dev$Other), collapse = "\n")))

```

### `r i18n$t("One positive thing about InnerSource")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.dev$`One positive thing`), collapse = "\n")))

```

<!-- ############################## -->
```{r include=FALSE}
i18n$set_translation_language("en")
```


# `r  i18n$t("Results of InnerSource Obstacles Survey")`

## `r i18n$t("Obstacles noted by the Managers")`

### `r i18n$t("From Survey Questions")`

```{r echo=FALSE, fig.show="hold", out.width="90%", fig.align="center", fig.width=12, fig.height=7}
what = i18n$t("Don't know what InnerSource is")
benefit = i18n$t("Not sure about the benefits of InnerSource")
resource = i18n$t("Lack of resource to allow cross-contribution")
quality = i18n$t("Unsure about Quality of outsider contributions")
responsible = i18n$t("Customer Service Impact from not knowing buggy code creator")
man_struct = i18n$t("Potential change in Management structure disrupting workflow")
budget = i18n$t("Budget Allocation for InnerSource")

colnames(f.man) = c('type', 'name', what, benefit, resource, quality, responsible, man_struct, budget, 'Other', 'One positive thing')
lv = data.frame(lapply(f.man[,3:9], process.lik))
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=17)) + guides(fill=guide_legend("")) + ggtitle(paste0('N=',nrow(f.man)))

```

### `r i18n$t("Other Obstacles")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.man$Other), collapse = "\n")))

```

### `r i18n$t("One positive thing about InnerSource")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.man$`One positive thing`), collapse = "\n")))

```

## `r i18n$t("Obstacles noted by the Repository Owners")`

### `r i18n$t("From Survey Questions")`

```{r echo=FALSE, fig.show="hold", out.width="90%", fig.align="center", fig.width=12, fig.height=7}
patcher = i18n$t("Lack of people submitting patches (lack of community)")
responsibility = i18n$t("Unsure about the Responsibilities")
mentor = i18n$t("Lack of time for Mentoring")
steal = i18n$t("Code 'Stolen' without proper credit")
publish = i18n$t("Don't want to publish code for InnerSource")
good = i18n$t("Don't know what's appropriate for InnerSource")
manager = i18n$t("Lack of support from Line Manager")
learn = i18n$t("Steep Learning Curve")
breaking = i18n$t("Breaking Changes affecting unknown consumers")
incentive = i18n$t("Incentives aren't appropriate")
  
colnames(f.own) = c('type', 'name', quality, patcher, responsibility, mentor, steal, publish, good, manager, learn, breaking, incentive, 'Other', 'One positive thing')
lv = data.frame(lapply(f.own[,3:13], process.lik))
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=17)) + guides(fill=guide_legend(""))+ ggtitle(paste0('N=',nrow(f.own)))

```

### `r i18n$t("Other Obstacles")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.own$Other), collapse = "\n")))

```

### `r i18n$t("One positive thing about InnerSource")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.own$`One positive thing`), collapse = "\n")))

```

## `r i18n$t("Obstacles noted by the Developers")`

### `r i18n$t("From Survey Questions")`

```{r echo=FALSE, fig.show="hold", out.width="90%", fig.align="center", fig.width=12, fig.height=7}
howc = i18n$t("Don't know how to contribute to InnerSource")
timel = i18n$t("Don't have time to contribute to InnerSource")
project = i18n$t("Project are uninteresting")
judge = i18n$t("Being judged for mistakes")

colnames(f.dev) = c('type', 'name', what, howc, manager, incentive, timel, learn, project, judge, 'Other', 'One positive thing')
lv = data.frame(lapply(f.dev[,3:10], process.lik))
lk = likert(lv)
plot(lk, centered=T, plot.percents =T, text.size=4, wrap=30, plot.percent.neutral=F, plot.percent.low=T, plot.percent.high=T) + theme(text = element_text(size=17)) + guides(fill=guide_legend("")) + ggtitle(paste0('N=',nrow(f.dev)))


```

### `r i18n$t("Other Obstacles")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.dev$Other), collapse = "\n")))

```

### `r i18n$t("One positive thing about InnerSource")`

```{r, echo=FALSE, results="asis"}
cat(str_to_sentence(paste("* ",na.omit(f.dev$`One positive thing`), collapse = "\n")))

```